Reintroduction of resistant frogs facilitates landscape-scale recovery in the presence of a lethal fungal disease

### 2024-09-26 doc/manuscript/supplementary_information.qmd
Buffer equation number in main text. Auto table update

| **Parameter^a^** | **Value** | **Source** |
|:---|:---|:---|
| $\sigma_{L_1}$, Yearly survival probability of year-1 tadpoles | 0.7 | Estimated from field data, observations |
| $\sigma_{L_2}$, Yearly survival probability of year-2 tadpoles | 0.7 | Estimated from field data, observations |
| $\sigma_{L_3}$, Yearly survival probability of year-3 tadpoles | 0.7 | Estimated from field data, observations |
| $\sigma_{J_1}$, Yearly survival probability of year-1 juveniles. | Varies yearly | Varies. Bounds estimated from field data, observations |
| $\sigma_{J_2}$, Yearly survival probability of year-2 juveniles | 0.5 | Estimated from field data, observations |
| $\sigma_{A_R}$, Yearly survival probability of naturally recruited adults | Varies by population | Estimated from CMR studies |
| $\sigma_{A_T}$, Yearly survival probability of translocated adults | Varies by population | Estimated from CMR studies |
| $p_{L_1}$, Probability of a year-1 tadpoles remaining as a tadpoles | 1 | Estimated from field data, observations |
| $p_{L_2}$, Probability of a year-2 tadpoles remaining as a tadpoles | 0.25 | Estimated from field data, observations |
| $p_{J_1}$, Probability of a year-1 juvenile remaining as a juvenile | 0.25 | Estimated from field data, observations |
| $p_F$, Probability of an adult female reproducing in a year | 0.5 | Could be as high at 1, based on field observations |
| $\rho$, Proportion of adults that are female | 0.5 | Estimated from field data |
| $F$, Number of surviving eggs produced by an adult female | 100 | From observations of captive frogs |

>>>>

| **Parameter^a^**                                                          | **Value**            | **Source**                                             |
|:--------------------------------------------------------------------------|:---------------------|:-------------------------------------------------------|
| $\sigma_{L_1}$, Yearly survival probability of year-1 tadpoles            | 0.7                  | Estimated from field data, observations                |
| $\sigma_{L_2}$, Yearly survival probability of year-2 tadpoles            | 0.7                  | Estimated from field data, observations                |
| $\sigma_{L_3}$, Yearly survival probability of year-3 tadpoles            | 0.7                  | Estimated from field data, observations                |
| $\sigma_{J_1}$, Yearly survival probability of year-1 juveniles.          | Varies yearly        | Varies. Bounds estimated from field data, observations |
| $\sigma_{J_2}$, Yearly survival probability of year-2 juveniles           | 0.5                  | Estimated from field data, observations                |
| $\sigma_{A_R}$, Yearly survival probability of naturally recruited adults | Varies by population | Estimated from CMR studies                             |
| $\sigma_{A_T}$, Yearly survival probability of translocated adults        | Varies by population | Estimated from CMR studies                             |
| $p_{L_1}$, Probability of a year-1 tadpoles remaining as a tadpoles       | 1                    | Estimated from field data, observations                |
| $p_{L_2}$, Probability of a year-2 tadpoles remaining as a tadpoles       | 0.25                 | Estimated from field data, observations                |
| $p_{J_1}$, Probability of a year-1 juvenile remaining as a juvenile       | 0.25                 | Estimated from field data, observations                |
| $p_F$, Probability of an adult female reproducing in a year               | 0.5                  | Could be as high at 1, based on field observations     |
| $\rho$, Proportion of adults that are female                              | 0.5                  | Estimated from field data                              |
| $F$, Number of surviving eggs produced by an adult female                 | 100                  | From observations of captive frogs                     |
